A Large-Scale Study of the Use of Eval in R

### 2020-08-24 inst/analysis/corpus-analysis.Rmd
Filled some misses

```{r}
overview_table(
  r("all programs", nrow(kaggle_finished) + sum(corpus_programs_files)),
  r("all runnbale code", sum(kaggle_code) + sum(runnable_code))
)
```

>>>>

```{r}
overview_table(
  r("all programs", nrow(kaggle_finished) + sum(corpus_programs_files)),
  r("all runnbale code", sum(kaggle_code) + sum(runnable_code)),
  r("all code", sum(kaggle_code) + sum(corpus_code) + sum(runnable_code))
)
```

### 2020-08-24 inst/paper/main.tex
Filled some misses

\begin{abstract}
  The \eval function turns text into code. From the point of view of
  reasoning about software system, uses of \eval turn the program's code
  from a statically known quantity that can be reasoned about and analyzed
  into one of the inputs to the program. Thus, widespread use of \eval
  hinders our ability to provide safety and security guarantees for
  software. Understanding how \eval is used in practice is key to finding
  ways to mitigate its damage. One question that has not been studied is
  whether the usage of \eval is dependent on the application domain or other
  features of the language. This paper is a large-scale study of a corpus of
  \miss{3} million lines of data science libraries and end-user written in
  the R language. We performed a simple static analysis and more
  sophisticated dynamic analysis to confirm that \eval is indeed in wide
  spread use, and to categorized patters of usage. We found that \eval in
  this code base is more dangerous in some ways, and safer in others, than
  what was previously reported for JavaScript.
\end{abstract}

@@

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above consider that R uses lazy evaluation like Haskell. The authors
  have informally surveyed end-users, including computer scientists, and did
  not find a single one aware of this fact. Library developers, on the other
  hand, know about laziness and program defensively around it.}  Thus, our
corpus distinguished between \emph{core packages} (there are \miss{8} such
packages that are loaded together with the R virtual machine), \emph{CRAN
  packages} (we selected \miss{500} curated packages that pass stringent
community quality checks and are equipped with tests and sample data),
\emph{scripts} (we used \miss{400} end-user written programs that performs a
particular data analysis task).  There are reasons to believe that \eval
usage patterns may differ between these datasets. The core R code is
extremely stable, it has only been maintained for the last 20 years with
very few far reaching changes. The libraries represent a more lively
ecosystem with new libraries added each day.  Finally, end user code is
often one-use scripts thrown together and sometimes never revisited.

@@

Over all, we observed \AllAllCallCountRnd call to \eval in \miss{3,000} runs
of our corpus. The mean number of calls per run was \miss{20} (with a min of
\miss{1} and a max of \miss{10,000}). Table~\ref{A} details the usage of
\eval across the corpus.  The format is T (m/M/x) where T is the total
number of calls observed for all runs of the corpus, m and x are the minimum
and maximum number of calls for any given run, and A is the mean number of
calls per run.  We can observe \miss{???}. {\bf <The following is a place
  holder. Real text will come once we have the table.>} The majority of
calls come from the core packages.  Kaggle does not have any own calls, any
\eval in those happens in dependent packages and core.  Of the
\missingNumber packages in our corpus, only \missingNumber packages call
eval.

>>>>

\begin{abstract}
  The \eval function turns text into code. From the point of view of
  reasoning about software system, uses of \eval turn the program's code
  from a statically known quantity that can be reasoned about and analyzed
  into one of the inputs to the program. Thus, widespread use of \eval
  hinders our ability to provide safety and security guarantees for
  software. Understanding how \eval is used in practice is key to finding
  ways to mitigate its damage. One question that has not been studied is
  whether the usage of \eval is dependent on the application domain or other
  features of the language. This paper is a large-scale study of a corpus of
  \CorpusAllCodeRnd lines of data science libraries and end-user written in
  the R language. We performed a simple static analysis and more
  sophisticated dynamic analysis to confirm that \eval is indeed in wide
  spread use, and to categorized patters of usage. We found that \eval in
  this code base is more dangerous in some ways, and safer in others, than
  what was previously reported for JavaScript.
\end{abstract}

@@

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above consider that R uses lazy evaluation like Haskell. The authors
  have informally surveyed end-users, including computer scientists, and did
  not find a single one aware of this fact. Library developers, on the other
  hand, know about laziness and program defensively around it.}  Thus, our
corpus distinguished between \emph{core packages} (there are \CorpusCorePackages such
packages that are distributed together with the R virtual machine), \emph{CRAN
  packages} (we selected \CorpusPackages curated packages that pass stringent
community quality checks and are equipped with tests and sample data),
\emph{Kaggle scripts} (we used \CorpusFinishedKaggle end-user written programs that performs a
particular data analysis task). There are reasons to believe that \eval
usage patterns may differ between these datasets. The core R code is
extremely stable, it has only been maintained for the last 20 years with
very few far reaching changes. The libraries represent a more lively
ecosystem with new libraries added each day.  Finally, end user code is
often one-use scripts thrown together and sometimes never revisited.

@@

Over all, we observed \AllAllCallCountRnd call to \eval in \CorpusAllProgramsRnd
programs in our corpus. The mean number of calls per run was \miss{20} (with a
min of \miss{1} and a max of \miss{10,000}). Table~\ref{A} details the usage of
\eval across the corpus. The format is T (m/M/x) where T is the total number of
calls observed for all runs of the corpus, m and x are the minimum and maximum
number of calls for any given run, and A is the mean number of calls per run. We
can observe \miss{???}. {\bf <The following is a place holder. Real text will
  come once we have the table.>} The majority of calls come from the core
packages. Kaggle does not have any own calls, any \eval in those happens in
dependent packages and core. Of the \missingNumber packages in our corpus, only
\missingNumber packages call eval.
